---
title: "iteration_and_listcols"
author: "Shan Jiang"
date: "10/30/2018"
output: github_document
---
* The **loop** basic structure in the course:
input = list(...)
      output = list(...)
      for (i in 1:n) {
            output[[i]] = f(input[[i]])
}

* The **map** basic structure:
      output = map(input, f)
* matrixs should be all of the same type of data(all numbers/ chracters)

```{r}
library(tidyverse)
set.seed(1)
```

# list
```{r}
# You can contain anything in a list.
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l
l[[2]]
```

# For loops
```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)
is.list(df)
```

Let's get a function!

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

```

We can apply the function to our `df`.
```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
#how to simplify the above functions?
```
Write a for loop?

```{r}
# You should specify the output in advance, it's needed and good.
output = vector("list", length = 4)
for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}

output
```

# Map Statements

let's replace the `for` loop with `map`.

```{r}
# only apply to first three elements 
df %>% 
  select(a, b, c) %>% 
  map(mean_and_sd)

#apply to the whole dataframe 
output = map(df, mean_and_sd)

```

Let's try a different function.
```{r}
# By using the summary
output = map(df, summary)
output 
```

## Map variant 
```{r}
# To produce a dataframe in the map function 
output = map_df(df, mean_and_sd)
output 
# To specify the double one 
output = map_dbl(df, mean_and_sd)
```

## Code Syntax

Be clear about the arguments!
```{r}
output = map(.x = df, ~ mean_and_sd(x = .x))
output 
# The na.rm only works for mean 
output = map_dbl(.x = df, ~ mean(x = .x, na.rm = F))
output
```


Learning Assessment

# Revisiting Napoleon
```{r}
library(rvest)

read_page_reviews <- function(url) {
  
  h = read_html(url)
  
  title = h %>%
    html_nodes("#cm_cr-review_list .review-title") %>%
    html_text()
  
  stars = h %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("\\d") %>%
    as.numeric()
  
  text = h %>%
    html_nodes(".review-data:nth-child(4)") %>%
    html_text()
  
  data_frame(title, stars, text)
}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(url_base, 1:5)

```
Read the page reviews in first 5 pages 
```{r}
read_page_reviews(vec_urls[[1]])
# Get a long collection of the reviews 
reviews = map(vec_urls, read_page_reviews)
```

# List Columns
Review the weather dataset
```{r}
library(rnoaa)

weather = 
  meteo_pull_monitors(c("USW00094728", "USC00519397", "USS0023B17S"),
                      var = c("PRCP", "TMIN", "TMAX"), 
                      date_min = "2016-01-01",
                      date_max = "2016-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY", 
                      USC00519397 = "Waikiki_HA",
                      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
#Central_Park = weather %>% filter()
weather_nest = 
 weather %>% 
  nest(date:tmin)
```

Pull out the name/ id in the nested data
```{r}
weather_nest %>% 
   pull(name)
weather_nest %>% 
   pull(id)
weather_nest %>% 
   pull()
```



