---
title: "iteration_and_listcols"
author: "Shan Jiang"
date: "10/30/2018"
output: github_document
---
* The **loop** basic structure in the course:
input = list(...)
      output = list(...)
      for (i in 1:n) {
            output[[i]] = f(input[[i]])
}

* The **map** basic structure:
      output = map(input, f)
* matrixs should be all of the same type of data(all numbers/ chracters)

```{r}
library(tidyverse)
set.seed(1)
```

# list
```{r}
# You can contain anything in a list.
l = list(vec_numeric = 5:8,
         mat         = matrix(1:8, 2, 4),
         vec_logical = c(TRUE, FALSE),
         summary     = summary(rnorm(1000)))
l
l[[2]]
```

# For loops
```{r}
df = data_frame(
  a = rnorm(20, 3, 1),
  b = rnorm(20, 0, 5),
  c = rnorm(20, 10, .2),
  d = rnorm(20, -3, 1)
)
is.list(df)
```

Let's get a function!

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}

```

We can apply the function to our `df`.
```{r}
mean_and_sd(df[[1]])
mean_and_sd(df[[2]])
#how to simplify the above functions?
```
Write a for loop?

```{r}
# You should specify the output in advance, it's needed and good.
output = vector("list", length = 4)
for (i in 1:4) {
  output[[i]] = mean_and_sd(df[[i]])
}

output
```

# Map Statements

let's replace the `for` loop with `map`.

```{r}
# only apply to first three elements 
df %>% 
  select(a, b, c) %>% 
  map(mean_and_sd)

#apply to the whole dataframe 
output = map(df, mean_and_sd)

```

Let's try a different function.
```{r}
# By using the summary
output = map(df, summary)
output 
```

## Map variant 
```{r}
# To produce a dataframe in the map function 
output = map_df(df, mean_and_sd)
output 
# To specify the double one 
output = map_dbl(df, mean_and_sd)
```

## Code Syntax 